### 2012-04-26 docs/compilers/compilers.tex
update Cray
fix typo

So far, no luck with these compilers (versions 7.4.3 and 8.0.0.135).

@@

Probably the best compilers for \maestro.  
Some notes:
\begin{itemize}
\item gfortran 4.5 has no known issues.
\item gfortran 4.6.1 and 4.6.2 on Fedora (15 and 16) have a bug that 
shows up in multi-processor runs ({\tt toy\_convect} on 4 processors, for instance).
The symptom is a crash during initialization with the message that
``message sizes do not match across processes in the collective'' in a
{\tt parallel\_bcast} call.  This is in {\tt cluster\_f.f90}, and the issue seems
to be a multiplication error in computing the size to allocate {\tt bxs}.
The bug is not present when you compile in debug mode, so it seems to be
related to optimization.
\end{itemize}

>>>>

Cray 8.0.2 compiles and runs \maestro\ fine on the interlagos/jaguarpf 
machine at OCLF.

@@

Probably the best compilers for \maestro.  
Some notes:
\begin{itemize}
\item gfortran 4.5 has no known issues.
\item gfortran 4.6.1--4.6.3 on Fedora (15 and 16) have a bug that 
shows up in multi-processor runs ({\tt toy\_convect} on 4 processors, for instance).
The symptom is a crash during initialization with the message that
``message sizes do not match across processes in the collective'' in a
{\tt parallel\_bcast} call.  This is in {\tt cluster\_f.f90}, and the issue seems
to be a multiplication error in computing the size to allocate {\tt bxs}.
The bug is not present when you compile in debug mode, so it seems to be
related to optimization.
\end{itemize}
